---
title: "importfx"
author: "Fendi Tsim"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
    toc_depth: 4
    vignette: >
      %\VignetteIndexEntry{introduction}
      %\VignetteEngine{knitr::rmarkdown}
      %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

`importfx` allows user to import specific user-defined functions from another R script. In this package there are two functions: `import` and `lookup`.

## Notes
Both functions produce unexpected results if there is a print/cat command with the word "function" as part of a string in R script that functions are imported from. Thus, use these functions with caution.

## import()

`import` allows user to decide which function(s) should be included or excluded when importing to the environment from another R script.

### Examples

Suppose a .R file (`functions.R`) in current directory contains following functions (`foo1`, `foo2`, `foo3`):

```{r echo=TRUE, results='hide'}
file.create("functions.R")  # Create a R script called 'functions.R'
writeLines(text = "foo1 <- function(){}\nfoo2 <- function(){}\nfoo3 <- function(){}", 
           con = file("functions.R")
           )
close(file("functions.R"))
```

Loading `importfx` package:

```{r setup}
library(importfx)
```

#### Import specific functions

The following command imports specific functions (`foo1` and `foo3`) from functions.R.

```{r}
import(from = "functions.R", only = c("foo1", "foo3"))
ls.str()  # Print objects in envir
rm(list = ls()) # Clean envir
```

Thus, `foo1` and `foo3` are imported in the Global environment.

#### Import all functions except specific functions

The following command shows imports all functions from functions.R except `foo1` and `foo3`.

```{r}
import(from = "functions.R", except = c("foo1", "foo3"))
ls.str()  # Print objects in envir
rm(list = ls()) # Clean envir
```

Thus, only `foo2` is imported in the Global environment.

#### Import functions that do not exist

Running the following code shows an error message as function(s) imported do not exist.

```{r echo='TRUE'}
import(from = "functions.R", only = c("foo1", "foo03"))
```

An error message is displayed when importing specific functions unsuccessfully.

```{r}
ls.str()  # Print objects in envir
```

Note that despite `foo1` is in functions.R, it is not imported in Global environment via above command.

#### Import all functions

The following command shows imports all functions from functions.R like `source(file = "functions.R")`.

```{r}
import(from = "functions.R")
ls.str()  # Print what exists in Global Environment
```

## lookup()

`lookup` provides names of all user-defined functions from another R script.

### Example

```{r}
lookup(from = "functions.R")
```