---
title: "importfx"
author: "Fendi Tsim"
date: "2023-08-08"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## **Introduction**

`importfx` package works similar to import function in Python.

At the start of a R script, user can decide which function(s) should be included or excluded when importing to the environment from another R script.

**Note that it is recommended to use this package at the start of running a R script (similar to Python) to prevent any current function objects in the environment being removed during importing.**

## **Examples**

Suppose a .R file (`functions.R`) in current directory contains following functions (`foo1`, `foo2`, `foo3`):

```{r}
file.create("functions.R")  # Create a R script called 'functions.R'
writeLines(text = "foo1 <- function(){}\nfoo2 <- function(){}\nfoo3 <- function(){}", 
           con = file("functions.R")
           )
close(file("functions.R"))
```

Loading `importfx` package:

```{r setup}
library(importfx)
```

### **Import specific functions**

The following command imports specific functions (`foo1` and `foo3`) from functions.R.

```{r}
import(file = "functions.R", only = c("foo1", "foo3"))
ls.str()  # Print what exists in Global Environment
```

Thus, `foo1` and `foo3` are imported in the Global environment.

### **Import all functions except specific functions**

The following command shows imports all functions from functions.R except `foo1` and `foo3`.

```{r}
import(file = "functions.R", except = c("foo1", "foo3"))
ls.str()  # Print what exists in Global Environment
```

Thus, only `foo2` is imported in the Global environment.

### **Import functions that do not exist**

Running the following code shows an error message as function(s) imported do not exist.

```{r echo='TRUE'}
import(file = "functions.R", only = c("foo1", "foo03"))
```

An error message is displayed when importing specific functions unsuccessfully.

```{r}
ls.str()  # Print what exists in Global Environment
```
Note that despite `foo1` is in functions.R, it is not imported in Global environment via above command.

Remarks: `foo2` was imported by the command from previous section. 

### **Import all functions**

The following command shows imports all functions from functions.R like `source(file = "functions.R")`.

```{r}
import(file = "functions.R")
ls.str()  # Print what exists in Global Environment
```
